\large How resource abundance and stochasticity affect animals' spatial needs

### 2023-08-24 writing/manuscript.Rmd
minor change to a figure caption

```{r 5-5-reg, eval=TRUE, echo=FALSE, fig.cap="Effects of $\\e(R)$ and $\\var(R)$ on simulated spatial requirements. The relationships were estimated using a Generalized Additive Model for Location and Scale (Rigby and Stasinopoulos 2005; Stasinopoulos and Rigby 2007) with a Gamma family of distributions. The model accounted for the effects of $\\e(R)$ and $\\var(R)$ and the interaction effects between the two on both $\\e(H)$ and $\\var(H)$. Note the nonlinear decrease in $H$ as $\\e(R)$ increases and the increase in $H$ as $\\var(R)$ increases. Additionally, note how the variance in spatial needs increases with mean spatial needs.", out.width='100%'}
knitr::include_graphics('../figures/simulation-regression-plots.png')
```

@@

\noindent The concept of a home range has a long history in ecological research as an indicator of the space an animal requires to satisfy its essential requirements during a period of time [@burt_territoriality_1943], but home range analysis is not appropriate for animals which are not range-resident, such as migrating animals [e.g., @jonzen_rapid_2006; @geremia_migrating_2019; @abrahms_memory_2019] and nomadic animals [e.g., @morato_space_2016; @nandintsetseg_variability_2019]. Although here we quantify animal's spatial needs using 50% and 95% home-range estimates, we expect that similar conclusions can be drawn about the positional variance, $\vpos$, of animals that are not range-resident.In the case of animals that are range resident for short periods of time, we can model their movement and short-term spatial needs within distinct and discrete periods or using a sliding window approach (see the discussion section). Note, however, that although range-resident animals will generally have smaller positional variance ($\vpos$) than migratory and nomadic animals, $\vpos$ is not sufficient to distinguish between range residency, migration, and nomadism, since $\vpos$ determines the scale and size of an animal's movement but not its behavior. Instead, the animal's $\tau_p$, $\tau_v$, and $\bar v$ can help discriminate between different behaviors. Animals with a $\tau_p$ shorter than a year are likely range-resident, while animals with a $\tau_p$ on the order of a year are likely to be migratory (as long as their life expectancy is greater than a year). In contrast, when an animal's $\tau_p$ is on the order of its expected lifespan, it is most often nomadic, since it does not have an average position it returns to regularly.
-->

>>>>

```{r 5-5-reg, eval=TRUE, echo=FALSE, fig.cap="Effects of $\\e(R)$ and $\\var(R)$ on simulated spatial requirements. The relationships were estimated using a Generalized Additive Model for Location and Scale (GAMLS; Rigby and Stasinopoulos 2005; Stasinopoulos and Rigby 2007) with a Gamma location-scale family of distributions ($\\tt{mgcv\\!::\\!gammals})$. The model accounted for the effects of $\\e(R)$ and $\\var(R)$ and the interaction effects between the two on both the location (i.e., mean) of $H$ and its scale parameter. Note the nonlinear decrease in $H$ as $\\e(R)$ increases and the increase in $H$ as $\\var(R)$ increases. Additionally, note how the variance in spatial needs strongly increases with mean spatial needs.", out.width='100%'}
knitr::include_graphics('../figures/simulation-regression-plots.png')
```

@@

\noindent The concept of a home range has a long history in ecological research as an indicator of the space an animal requires to satisfy its essential requirements during a period of time [@burt_territoriality_1943], but home range analysis is not appropriate for animals which are not range-resident, such as migrating animals [e.g., @jonzen_rapid_2006; @geremia_migrating_2019; @abrahms_memory_2019] and nomadic animals [e.g., @morato_space_2016; @nandintsetseg_variability_2019]. Although here we quantify animal's spatial needs using 95% home-range estimates, we expect that similar conclusions can be drawn about the positional variance, $\vpos$, of animals that are not range-resident.In the case of animals that are range resident for short periods of time, we can model their movement and short-term spatial needs within distinct and discrete periods or using a sliding window approach (see the discussion section). Note, however, that although range-resident animals will generally have smaller positional variance ($\vpos$) than migratory and nomadic animals, $\vpos$ is not sufficient to distinguish between range residency, migration, and nomadism, since $\vpos$ determines the scale and size of an animal's movement but not its behavior. Instead, the animal's $\tau_p$, $\tau_v$, and $\bar v$ can help discriminate between different behaviors. Animals with a $\tau_p$ shorter than a year are likely range-resident, while animals with a $\tau_p$ on the order of a year are likely to be migratory (as long as their life expectancy is greater than a year). In contrast, when an animal's $\tau_p$ is on the order of its expected lifespan, it is most often nomadic, since it does not have an average position it returns to regularly.
-->
